Let’s Disco – Publishing person-level data as Linked Data.

### 2015-01-07 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
zechnical review publication bio

\section{Anweisungen}

Proposals should not exceed 5 pages using a reasonable font size (not less than 11 pts). They should include the call for participation together with the following details:
- Abstract: 200 words maximum, for inclusion to the ESWC 2015 Web site.
- Tutorial description: objectives of the tutorial and relevance to ESWC 2015; information about the scope and level of detail of the material to be covered; intended audiences; learning objectives; practical sessions.
- Tutorial length: Half or full day, including preferences.
- Previous versions or related tutorials: other venues of this or similar tutorials (potentially by a different team of tutors), motivation for offering the tutorial again, at the ESWC2015.
- Tutoring team: short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)

@@

The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data. Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage. Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.

@@

In different real world use cases, the workshop organizers demonstrate the adoption and inclusion of Disco in existing information systems. Workshop participants are encouraged to present their own use cases where Disco has been applied or will be used. Together with the workshop organizers, workshop participants will have the possibility to elaborate an RDF representation of their use cases and to formulate typical queries which are necessary to solve use case related problems.
The workshop has a technical perspective and addresses software developers as well as data publishers who want to publish DDI metadata as Linked Data. No prerequisites are necessary, since a short introduction to RDF and Linked Open Data will be given.

@@

@@

\subsection{Intended Audiences}
Linked Data experts that are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data

@@

Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} (M.Sc. in Computer Science) is a PhD student at Gesis - Leibniz Institute for the Social Sciences in Mannheim , Germany since 2010.
He studied Information Systems at the Technical University of Munich.
His general research topic is about RDF validation. 
He held multiple conference and workshop presentations (e.g. ISWC, DC, WWW, Dagstuhl seminars) in the last five years.

Benjamin Zapilko holds a degree in Computer Sceince and has recently finished his PhD thesis about methods for matching social science relevant Linked Data. The defense talk will be at the end of January. Beside his PhD research, he works on modelling and publishing social science relevant data as Linked Data with the focus on data modelling and integration of heterogeneous data sources and information types. He presented his work at several international conferences.

>>>>

%\section{Anweisungen}
%
%Proposals should not exceed 5 pages using a reasonable font size (not less than 11 pts). They should include the call for participation together with the following details:
%- Abstract: 200 words maximum, for inclusion to the ESWC 2015 Web site.
%- Tutorial description: objectives of the tutorial and relevance to ESWC 2015; information about the scope and level of detail of the material to be covered; intended audiences; learning objectives; practical sessions.
%- Tutorial length: Half or full day, including preferences.
%- Previous versions or related tutorials: other venues of this or similar tutorials (potentially by a different team of tutors), motivation for offering the tutorial again, at the ESWC2015.
%- Tutoring team: short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)

@@

In different real world use cases, the workshop organizers demonstrate the adoption and inclusion of Disco in existing information systems. 
Workshop participants are encouraged to present their own use cases where Disco has been applied or will be used. 
Together with the workshop organizers, workshop participants will have the possibility to elaborate an RDF representation of their use cases and to formulate typical queries which are necessary to solve use case related problems.
The workshop addresses software developers as well as data publishers who want to publish DDI metadata as Linked Data.

The DDI-RDF Discovery Vocabulary (Disco)\footnote{current specification is available at \url{https://github.com/linked-statistics/disco-spec}}  is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data. Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage. Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.

@@

@@

In 2012, we started the development of Disco in form of a one-week Dagstuhl seminar - another one-week Dagstuhl seminar and two one-week workshops followed.  
In 2014, we finished the technical review of Disco.
We addressed more than ten mailing lists from the Linked Data and the DDI communities and got feedback which has been incorporated into the Disco specification.
We are planning to officially publish Disco after three years of development in the first half of the year 2015 after an additional official technical review of the DDI Alliance\footnote{\url{http://www.ddialliance.org/}}.

@@

\subsection{Intended Audiences}
Linked Data experts that are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data.

@@

Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} studies information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
His research topic is all about RDF validation.
More specifically, he investigates how to validate any RDF constraints (formulated by multiple constraint languages) and how to express them generically. 
He held multiple presentations at international conferences and workshops (e.g. WWW, ISWC, DC, Dagstuhl seminars).

Benjamin Zapilko holds a degree in Computer Science and has recently finished his PhD thesis about methods for matching social science relevant Linked Data. The defense talk will be at the end of January. Beside his PhD research, he works on modelling and publishing social science relevant data as Linked Data with the focus on data modelling and integration of heterogeneous data sources and information types. He presented his work at several international conferences.
